---
title: "Model 8 Assignment"
author: "Jacob Fabian"
date: "2022-10-26"
output:
  pdf_document: default
  html_document: default
---
```{r}
library(lpSolveAPI)
library(ucminf)
library(Benchmarking)
library(ggplot2)
```


###CRS

```{r}
x <- matrix(c(150,400,320,520,350,320,0.2,0.7,1.2,2,1.2,0.7),ncol = 2)
y <- matrix(c(14000,14000,42000,28000,19000,14000,3500,21000,10500,42000,25000,15000), ncol=2)
z <- dea(x,y,RTS = "crs")
z
peers(z)
lambda(z)
rowSums(x)
rowSums(y)
dea.plot( rowSums(x),rowSums(y),RTS="crs")
a <- as.data.frame(matrix(c(x,y),ncol=4))
a
ggplot(data=a,aes(V2,V3)) +
  geom_line(aes(color="red")) +
  geom_line(aes(V2,V4),color="yellow",show.legend = T)
```
### Facility 1-4 are efficient. Facility 5-6 are not efficient. 


###VRS


```{r}
x <- matrix(c(150,400,320,520,350,320,.2,.7,1.2,2,1.2,.7),ncol = 2)
y <- matrix(c(14000,14000,42000,28000,19000,14000,3500,21000,10500,42000,25000,15000), ncol=2)
z <- dea(x,y,RTS = "vrs")
z
peers(z)
lambda(z)
rowSums(x)
rowSums(y)
dea.plot( rowSums(x),rowSums(y),RTS="vrs",wx=0.01,wy=0.01)
```

### Facility 6 is inefficient.


###IRS

```{r}
x <- matrix(c(150,400,320,520,350,320,.2,.7,1.2,2,1.2,.7),ncol = 2)
y <- matrix(c(14000,14000,42000,28000,19000,14000,3500,21000,10500,42000,25000,15000), ncol=2)
z <- dea(x,y,RTS = "irs")
z
peers(z)
lambda(z)
rowSums(x)
rowSums(y)
dea.plot( rowSums(x),rowSums(y),RTS="irs",wx=0.01,wy=0.01)
```
### Facility 6 is inefficient. 



###DRS

```{r}
x <- matrix(c(150,400,320,520,350,320,.2,.7,1.2,2,1.2,.7),ncol = 2)
y <- matrix(c(14000,14000,42000,28000,19000,14000,3500,21000,10500,42000,25000,15000), ncol=2)
z <- dea(x,y,RTS = "drs")
z
peers(z)
lambda(z)
rowSums(x)
rowSums(y)
dea.plot( rowSums(x),rowSums(y),RTS="drs",wx=0.01,wy=0.01)
```
### Both facility 5 and 6 are inefficient, Facility 5 could be updated by closing to the facility 1,2 and 4. Facility 6 should be updated by using the facility 1,2 and 4. Both coeficients should be the lambda values. 

###FDH

```{r}
x <- matrix(c(150,400,320,520,350,320,.2,.7,1.2,2,1.2,.7),ncol = 2)
y <- matrix(c(14000,14000,42000,28000,19000,14000,3500,21000,10500,42000,25000,15000), ncol=2)
z <- dea(x,y,RTS = "fdh", ORIENTATION = 2)
z
peers(z)
lambda(z)
rowSums(x)
rowSums(y)
dea.plot( rowSums(x),rowSums(y),RTS="fdh",wx=0.01,wy=0.01)
```
### All facilities are efficient. 


##FDH
```{r}
x <- matrix(c(150,400,320,520,350,320,.2,.7,1.2,2,1.2,.7),ncol = 2)
y <- matrix(c(14000,14000,42000,28000,19000,14000,3500,21000,10500,42000,25000,15000), ncol=2)
z <- dea(x,y,RTS = "fdh", ORIENTATION = 2)
z
peers(z)
lambda(z)
rowSums(x)
rowSums(y)
dea.plot( rowSums(x),rowSums(y),RTS="fdh",wx=0.01,wy=0.01)
```
### All facilities are efficient. 

###FRH

```{r}
x <- matrix(c(150,400,320,520,350,320,.2,.7,1.2,2,1.2,.7),ncol = 2)
y <- matrix(c(14000,14000,42000,28000,19000,14000,3500,21000,10500,42000,25000,15000), ncol=2)
z <- dea(x,y,RTS = "add")
z
peers(z)
lambda(z)
rowSums(x)
rowSums(y)
dea.plot( rowSums(x),rowSums(y),RTS="add",wx=0.01,wy=0.01)
```
### All facilities are all efficient

### CRS - Facility 1-4 are efficient. Facility 5-6 are not efficient. 
### VRS - Facility 6 is inefficient.
### IRS - Facility 6 is inefficient. 
### DRS - Both facility 5 and 6 are inefficient. Both coeficients should be the lambda values
### FDH - All facilities are efficient.
### FRH - All facilities are efficient
### Under VRS and IRS, the peers unit for inefficient facilities were 1,2 and 5.
### Under CRS and DRS, the peers unites were 1,2,and 4. 




